---
title: "Team_Essay_2"
author: "Sahil, Ariel, Ilya, Lekha, Anthony, Trang"
date: "3/6/2021"
output: pdf_document
---

## Introduction

## Formula and Basics

Multiple linear regression: y = $\beta_0$ + $\beta_1x_1$ + $\beta_2x_2$ +...+$\beta_kx_k$ + $\epsilon$

-   $\beta_0$ is value of y when all $x_k$ are equal to zero
-   $\beta_k$ are beta coefficients which measure the correlation between the result and it's predictor variables
-   $x_k$ are the independent variables
-   $\epsilon$ is the error term, the part of y that can be explained through the regression model.

## Loading Required R Packages

-   readxl - to read data from xl
-   tidyverse - for data visualization and manipulation
-   rlist - to compute rmse

```{r}
library("tidyverse") 
library("readxl")
library("rlist")
```

## Data Description

Examples of Data and problem:

```{r}
bball_data <- read_excel("Basketball.xlsx")
bball_data <- bball_data %>%
  rename(
    "height" = "X1",
    "weight" = "X2",
    "FGP" = "X3",
    "FTP" = "X4",
    "PPG" = "X5"
  )
full_data = bball_data[1:55,]
bball_data
```

## Visualization

## Analysis

## Computation

-   Height_Model: `height = b0 + b1*weight + b2*FGP + b3*FTP + b4*PPG`

```{r}
bball_data <- read_excel("Basketball.xlsx")
bball_data <- bball_data %>%
  rename(
    "height" = "X1",
    "weight" = "X2",
    "FGP" = "X3",
    "FTP" = "X4",
    "PPG" = "X5"
  )
train_data = bball_data[1:30,]
test_data = bball_data[31:52,]
```

## Interpretation of the Model

```{r}
Height_Model <- lm(height ~ ., data = bball_data)
#Summary of the model
summary(Height_Model)
summary(Height_Model)$coefficient
#Confidence Interval of the model coefficients
confint(Height_Model)
#Coefficient of determination
summary(Height_Model)$r.squared
#RSE
sigma(Height_Model)/mean(bball_data$height)
plot(Height_Model)
```

From the output for above Height_Model:

We can see that resulting regression equation is:

-   `height = 3.798049837 + 0.011489032*weight + 1.138889566*FGP - 0.049315550*FTP - 0.008273347*PPG`
-   b0 = 3.798049837
-   b1 = 0.011489032
-   b2 = 1.138889566
-   b3 = 0.049315550
-   b4 = -0.008273347

We also observe that weight is the significant predictor.

## Model Evaluation

Training model

```{r}
train_model <-lm(height ~ ., data = train_data)
train_pred <- predict(train_model, train_data)
rmse(train_pred, train_data$height)
res <- train_pred - train_data$height
sum(res)
plot(train_model)
```

-   The RMSE for training model is 0.2208217.
-   The sum of residuals for training model is -1.865175e-14.

Testing Model

```{r}
test_model <-lm(height ~ ., data = test_data)
test_pred <- predict(train_model, test_data)
rmse(test_pred, test_data$height)
res2 <- test_pred - test_data$height
sum(res2)
plot(test_model)
```

-   The RMSE for testing model is 0.2863395. (This is pretty good)
-   The sum of residuals for testing model is 1.664502. (This could have been better)

## Model Assessment

```{r}
summary(train_model)
sigma(train_model)/mean(train_data$height)
```

We can see that our model has the following indicators:

-   Residual standard error: 0.2419 on 25 degrees of freedom (The more it is closer to 1 the better)
-   Multiple R-squared: 0.6355 (Higher the better)
-   Adjusted R-squared: 0.5772 (Higher the better)
-   F-statistic: 10.9 on 4 and 25 DF (Higher the better)
-   p-value: 2.967e-05 (Lower the better)
-   RSE: 0.03641216 (Lower the better)

## Interpretation

Height_Model: `height = 3.798049837 + 0.011489032*weight + 1.138889566*FGP - 0.049315550*FTP - 0.008273347*PPG`

-   We can say that height = 3.798049837, when all the other predictors are set to 0.
-   In our model, it can be seen that p-value of the F-statistic is \< 1.41e-05, which is highly significant. This means that, at least, one of the predictor variables is significantly related to the outcome variable.
-   To see which predictor variables are significant, you can examine the coefficients table, which shows the estimate of regression beta coefficients and the associated t-statitic p-values:

```{r}
summary(train_model)$coefficient
```

-   For a given the predictor, the t-statistic evaluates whether or not there is significant association between the predictor and the outcome variable, that is whether the beta coefficient of the predictor is significantly different from zero.
-   It can be seen that, changing weight and PPG are significantly associated to changes in height while changes in FTP and FGP are not significantly associated with height.

```{r}
model2 <- lm(height ~ weight + PPG, data = bball_data)
summary(model2)
```

Removing FTP and FGP we get the following:

-   Residual standard error: 0.2563 on 51 degrees of freedom
-   Multiple R-squared: 0.6998
-   Adjusted R-squared: 0.688
-   F-statistic: 59.44 on 2 and 51 DF
-   p-value: 4.728e-14
-   There are few better changes but not as much as we expected.

## Model accuracy assessment

Height_Model: `height = 3.798049837 + 0.011489032*weight + 1.138889566*FGP - 0.049315550*FTP - 0.008273347*PPG`

1.  weight = 225, FGP = 0.482, FTP = 0.701, PPG = 11.6

-   Estimate of Height: 6.8
-   Actual: 6.8

2.  weight = 215, FGP = 0.457, FTP = 0.734, PPG = 5.8

-   Estimate of Height: 6.7
-   Actual: 6.8

3.  weight = 230, FGP = 0.435, FTP = 0.764, PPG = 8.3

-   Estimate of Height: 6.82
-   Actual: 7

## Read also

## Discussion

## References
